\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-07-01 paper.tex
Proof-reading Aurelie + Rachid

Execution control systems for social robots are expected 
to account not only for the task achievement but also for the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint}. {\sc Shary} supports
such mechanisms~\cite{Clodic2007smc}. It allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables the robot as well as the human to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms. In Shary, each action description contains not only the way to execute it and monitor it, but also the way to initiate it (e.g. in the case of a shared action, the way both agents need to commit to the task), to suspend (or cancel or stop) it (and for each case the way this transition has to be shared with the human partner if any). This is supported by a description of the beliefs of each involved agent concerning the action achievement process and a set of monitoring processes allowing to update it

@@

These five questions should not be considered independently from each other and
often require, on the contrary, to be dealt with in a single decision step. The
human-aware task and motion planners which we have built, are instances of
systems which have been designed to deal with such intricate decision issues.

They are in fact taken into account in most, if not in all, the
components and at different levels of abstraction: at the shared plan
level as well as at action refinement and execution level.

Repeatedly, the choice of the next action, of who has to act (the human, the robot
or both of them) and when to perform it is made by {\sc Shary} with
the help of {\sc HATP}, based on perspective-taking and
situation assessment ({\sc Spark} and {\sc Oro} as well as on
estimation of the human mental state ({\sc Shary} with the help of
{\sc Oro}).

Where and how to perform an action is made by a full set of on-line
planning functions provided by {\sc Mhp} that computes not only
trajectories but also the pertinent placements and postures based not
only on geometric information but also estimation of the human current
mental state and preferences ({\sc Oro}).

>>>>

Execution control systems for social robots are expected 
to account not only for the task achievement but also for the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint}. {\sc Shary} supports
such mechanisms~\cite{Clodic2007smc}. It allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables the robot as well as the human to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference mechanisms. In {\sc Shary},
each action description contains not only how to execute it and monitor it,
but also how to initiate it (\eg in the case of a shared action, how
both agents need to commit to the task) and how to suspend (or cancel) it. In
each of these cases, the action description also makes explicit how the
transition has to be communicated to the human partner if necessary. This is
supported by a description of the beliefs of each of the agents
regarding the action achievement process, as well as a set of so-called
\emph{monitoring processes} that update them.

@@

These five questions should not be considered independently from each other and
often require, on the contrary, to be dealt with in a single decision step. The
human-aware task and motion planners which we have built are instances of
systems which have been designed to deal with such intricate decision issues.

They are in fact considered in each of the components, at different levels of
abstraction (from the abstract shared plan level to the action refinement and
execution level).  At every interaction step, the choice of the next action, of
who has to act (the human, the robot or both of them) and when to perform it is
made by {\sc Shary} with the help of HATP, based on perspective-taking and
situation assessment ({\sc Spark} and {\sc Oro} as well as on estimation of the
human mental state ({\sc Shary} with the help of {\sc Oro}). The actual
realization of the action is eventually supported by a full set of on-line
planning functions provided by {\sc Mhp} that computes not only trajectories but
also the pertinent placements and postures based not only on geometric
information but also estimation of the human current mental state and
preferences ({\sc Oro}).
